Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-21 tex/paper1/paper1.tex
edits to the paper

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the Fourier power spectra in each of the
  four regions studied in AIA 171\AA\ (left column) and AIA
  193\AA\ (right column).  Also shown are the posterior mean and
  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section
  \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
  Model fit parameter values and their 68\% credible intervals are
  quoted in Table \ref{tab:parameters}. See also Figure
  \ref{fig:fit193} for the corresponding AIA 193\AA\ plots.}
\label{fig:fit171}
\end{figure}

@@

The (geometric) mean Fourier power spectra are shown in Figures
\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.  The results for the
quiet Sun, loop footpoints and sunspot regions suggest a \PL\ \PS.
This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the \PL\ index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

Each emission event is modeled as an exponentially decaying function
of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{total}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
emission $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the total emission in each event depends on its time scale $T$
such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed \PS\ can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P_{total}(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}
This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar emission events.

@@

Future studies will include examining power spectra at many more
locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
131\AA and 211\AA\ wavebands.  The power-law index in
individual pixels will also be determined, and correlated with other
physical quantiies such as the emission from those pixels.

Finally, a better understanding of the source of the power-law power
spectrum will come from comparing the \Fps\ of simulated observations
to the \Fps\ of the data in all the AIA wave-bands that are sensitive
to higher temperatures.  This will bring new constraints on the
simulations and improve our understanding of the
temporal behavior of the solar corona.

@@

\section{Model fitting procedure}\label{sec:app:ind}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171} and
\ref{fig:fit193}.  The frequency $\nu$ is defined as $f/f_{0}$ where
$f$ is the FFT frequency in Hz, and $f_{0}$ is the lowest non-zero FFT
frequency defined by the data (Section \ref{sec:obs}).

>>>>

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the Fourier power spectra in each of the
  four regions studied in AIA 171\AA\ (left column) and AIA
  193\AA\ (right column).  Also shown are the posterior mean and
  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section
  \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
  Model fit parameter values and their 68\% credible intervals are
  quoted in Table \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

@@

The (geometric) mean Fourier power spectra are shown in Figure
\ref{fig:fit171193} for each of the physical regions considered.  It
is clear that, in general, the Fourier power spectra exhibit power-law
like characteristics.  The results for the quiet Sun, loop footpoints
and sunspot regions suggest a \PL\ \PS.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the \PL\ index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figure
\ref{fig:fit171193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

Each emission event is modeled as an exponentially decaying function
of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{total}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
emission $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the total emission in each event depends on its time scale $T$
such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed \PS\ can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P_{total}(\nu) \propto \nu^{-(2-\alpha_{E})(1+\gamma)}.
\end{equation}
This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar emission events.

@@

Future studies will include examining power spectra at many more
locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
131\AA and 211\AA\ wavebands.  The power-law index in individual
pixels will also be determined, and correlated with other physical
quantiies such as the emission from those pixels.  Finally, a better
understanding of the source of the power-law power spectrum will come
from comparing the \Fps\ of simulated observations to the \Fps\ of the
data in all the AIA wave-bands that are sensitive to higher
temperatures.  This will bring new constraints on the simulations and
improve our understanding of the temporal behavior of the solar
corona.

@@

\section{Model fitting procedure}\label{sec:app:ind}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).
